Review of Assigned Readings

### 2017-12-28 documentation/documentation.tex
added sources in intro, twitter, bib.file and abbreviations of bitcoin part

% List of abbreviations
\usepackage{acronym}

@@

    \begin{abstract}
    \pagenumbering{Roman}
    \begin{spacing}{1.5}

  (Insert text)

    \end{spacing}

    \end{abstract}

@@

    \listoffigures 	
    \section*{List of Abbreviation} 
	\begin{acronym}[ASECRETTT] 
	\acro{API}{Application Programming Interface}
	\acro{ATOKEN}{Access Token}
	\acro{ASECRET}{Access Token Secret}
	\acro{CKEY}{Consumer Key}
	\acro{CSECRET}{Consumer Secret}
	\acro{JSON}{Java Script Object Notation}
	\acro{RPI}{Raspberry Pi}
	\acro{SSH}{Secure Shell}
	\end{acronym}
    \clearpage

\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}
\section{Introduction}
In the academic environment accountability and reproducibility is important. However, the publishing process of papers and journals seem to be outdated. New ways of data collection and data processing exist by using computational economics. The usage of algorithms can increase effectiveness and efficiency. Hence, much lager data sets can be proceeded. However this creates also new problems regarding to traceability and reproducibility. Often cited academic paper exist, where the initial computation is not reproducible. Furthermore, some academic paper even contain computational errors. Replicating data or existing results do not provide any new knowledge at all. Nevertheless, the ability to reproduce increases trustworthiness and indicate the quality of the conducted work. This explains why reproduction is of great relevance.

@@

\section{Data Collection}
This section contains a detailed description of how the data for the sequential analysis is gathered and stored. This includes two  subsections the (1) tweets data and the (2) bitcoin price data.
\subsection{Tweets Data}
Whit the python script real-time twitter data are streamed and stored. This happens with help of a raspberry pi.
\subsubsection{Python Script}
Twitter offers different Application Programming Interfaces (API) for collecting data. However, the time frame for gathering data on a freely base is limited to 7 days. On the other hand, python offers different twitter libraries. Such as the open-source package tweepy. This package has been used for streaming the twitter data as it simplify the script.

@@

\paragraph{Twitter Authentication}\mbox{}\\{}
To access the twitter data, twitter requests an identification of the user. The identification is assured by different keys and access tokens. Those are the (1) consumer key (ckey), (2) consumer secret (csecret), (3) access token (atoken) and (4) access token secret (asecret).

To obtain the mentioned keys and tokens a twitter account is needed. Once, a twitter account exist a application has to be created. This has to be conducted by login with the twitter account credentials under the following link: 
\begin{lstlisting}[language=bash]
https://apps.twitter.com/
\end{lstlisting}

After the creation of a application, the keys and tokens can be extracted. Figure 1 illustrates how to retrieve the keys and tokens.
\begin{figure}[h]
\centering
\includegraphics[scale=0.6]{twitteraccess}
\caption{Twitter Keys and Access Tokens}
\end{figure}

@@

From the JSON format the following parameters are decoded:
\begin{itemize}
    \item created at: Timestamp of the created tweet
    \item text: text of the tweet
\end{itemize}
The time timestamps are in UTC time.

>>>>

% List of abbreviations
\usepackage {acronym}

@@

@@

    \listoffigures 	
    \section*{List of Abbreviation} 
	\begin{acronym}[ASECRETTT] 
	\acro{API}{Application Programming Interface}
	\acro{ATOKEN}{Access Token}
	\acro{ASECRET}{Access Token Secret}
	\acro{CKEY}{Consumer Key}
	\acro{CSECRET}{Consumer Secret}
	\acro{JSON}{Java Script Object Notation}
	\acro{RPI}{Raspberry Pi}
	\acro{SSH}{Secure Shell}
	\acro{BPI}{Bitcoin Price Index}
	\acro{BTC}{Bitcoin}
	\acro{USD}{US Dollar}
	\end{acronym}
    \clearpage

\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}
\section{Introduction}
In the academic environment accountability and reproducibility is important. However, the publishing process of papers and journals seem to be outdated as reproducability is not evaluated by many journals. (\cite{mccullough2013}) New ways of data collection and data processing exist by using computational economics. The usage of algorithms can increase effectiveness and efficiency. Hence, much lager data sets can be proceeded. However this creates also new problems regarding to traceability and reproducibility. Often cited academic paper exist, where the initial computation is not reproducible (\cite{mccullough2013}). Replicating data or existing results do not provide any new knowledge at all. Nevertheless, the ability to reproduce is key in science and non-reproducable work can not be characterized as science or used as a basis for policy making (\cite{mccullough2013}). This explains why reproduction is of great relevance.

@@

\section{Data Collection}
This section contains a detailed description of how the data for the sequential analysis is gathered and stored. This includes two  subsections the (1) tweets data and the (2) bitcoin price data.
\subsection{Tweets Data}
Whit the python script real-time twitter data are streamed and stored. This happens with help of a raspberry pi.
\subsubsection{Python Script}
Twitter offers different Application Programming Interfaces (API) for collecting data. However, the time frame for gathering data on a freely base with full access is limited to 7 days (\cite{twitterinc2017a}). On the other hand, python offers different twitter libraries. Such as the open-source package tweepy. This package has been used for streaming the twitter data as it simplify the script.

@@

\paragraph{Twitter Authentication}\mbox{}\\{}
To access the twitter data, twitter requests an identification of the user. The identification is assured by different keys and access tokens. Those are the (1) consumer key (CKEY), (2) consumer secret (CSECRET), (3) access token (ATOKEN) and (4) access token secret (ASECRET).(\cite{twitterinc2017b})

To obtain the mentioned keys and tokens a twitter account is needed. Once, a twitter account exist a application has to be created. This has to be conducted by login with the twitter account credentials under the following link: 
\begin{lstlisting}[language=bash]
%https://apps.twitter.com/
\end{lstlisting}

After the creation of a application, the keys and tokens can be extracted. Figure \ref{Fig:Keys and Tokens} illustrates how to retrieve the keys and tokens.
\begin{figure}[h]
\centering
\includegraphics[scale=0.6]{twitteraccess}
\caption{Twitter Keys and Access Tokens, based on \cite{twitterinc2017c}.}
\label{Fig:Keys and Tokens}
\end{figure}

@@

From the JSON format the following parameters are decoded:
\begin{itemize}
    \item created at: Timestamp of the created tweet
    \item text: Text of the tweet
\end{itemize}
The timestamps are in UTC time.
